Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2019-10-14 main_new.tex
Updated abstract

\begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task
  for marine science and maritime management. Faced with limited
  resources to understand dynamic processes in the water-column, the
  combination of statistics and autonomous robotics provide new
  opportunities for studying experimental design. In this work we develop
  methods for efficient spatial sampling applied to the mapping of
  coastal processes by providing informative descriptions of spatial
  characteristics of ocean phenomena. Specifically, we define a design
  criterion based on reducing uncertainty in the joint excursions of
  random fields, and derive analytical expressions for the expected
  Bernoulli variance reduction in the excursion set of spatial
  temperature and salinity variables, providing a description of
the boundary uncertainty that can be used to prioritize sampling efforts at locations that are
ambiguous, making exploration more effective. We show how these can be
  applicable in static and sequential designs, building on myopic and
  non-myopic sampling strategies. We use simulations to study the
  properties and differences between state-of-the-art approaches,
  followed by results from field deployments with an autonomous
  underwater vehicle as part of a case study mapping the boundary of a
  river plume. The results demonstrate the potential of combining statistical methods and robotic platforms, and the abilities of the derived methods to effectively inform and execute data-driven environmental sampling.

>>>>

\begin{abstract}
 \begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task for marine science and maritime management. Faced with limited resources to understand processes in the water-column, the combination of statistics and autonomous robotics provide new opportunities for experimental designs. In this work we develop methods for efficient spatial sampling applied to the mapping of coastal processes by providing informative descriptions of spatial characteristics of ocean phenomena. Specifically, we define a design criterion based on reducing uncertainty in the joint excursions of vector-valued Gaussian random fields, and derive tractable expressions for the expected Bernoulli variance reduction in such a framework. We demonstrate how these provide a description of the boundary uncertainty in temperature and salinity variables, which is used to prioritize sampling efforts at locations that are ambiguous, making exploration more effective by building on myopic and non-myopic strategies. We use simulations to study the properties and differences between state-of-the-art approaches, followed by results from field deployments with an autonomous underwater vehicle as part of a case study mapping the boundary of a river plume. The results demonstrate the potential of combining statistical methods and robotic platforms to effectively inform and execute data-driven environmental sampling.
